|

### 2022-05-17 Memo/memo.Rmd
update memo and appendix

The second reason is that adding control variables improves the efficiency of
our estimates \citep{calonico2019regression}. We add five controls to the main
specifications. We include the 2003 population because it conditions the
multiple threshold assignments. We add GDP per capita to control for Brazil's
economic expansion during the 2000s. We also add the number of seats in 2000 to
ensure that our results come from the current legislature size and not from past
seat allocations. Year was included in the models to control for seasonal
effects. Finally, we add a dummy for Northeast states. The Northeast region
received considerable attention from the Federal Government in the 2000s.
According to \citet{de2015politica}, in 2003 the Lula administration recreated
the Superintendency for the Development of the Northeast (SUDENE), investing BRL
84 Billion from 2003 to 2010. This amounts to around 70% of all targeted
regional investments. One example of these investments is that the Federal
Government created about 100 new universities in the Northeast region. Moreover,
infant mortality in the region decreased from 22.4 deaths per 1000 infants born
in 2005 to 19.6 deaths per 1000 infants born in 2008 due to larger federal
investments. In turn, education quality improved from 2.69 in 2005 to a 3.14
score in 2007 (0 to 10 quality of education score). For this reason, adding a
dummy for Northeast states is essential for ensuring the consistency and the
efficiency of our estimates.

@@

We collapse two concerns from Reviewer 3 since they both speak to core topics in
our paper. In Table 6 of the Supplementary Materials (page 21), we show that an
additional legislator usually does not lead to significant increases in public
expenditure. Therefore, our results speak more about the allocation of resources
than about government spending. In our section titled "Background on the
Brazilian Case" (page 14), we clarify why increasing the city council size often
results in a pro-mayor legislator. We write (page 15): "\textit{Brazil also
adopts a unique formula to allocate seats, which combines the Hare quota and the
D’Hondt method and strongly favors larger parties \citep{nicolau2015sistemas}.
This poses a major obstacle for small parties to reach the electoral quorum, so
they often join party coalitions to improve their chances of winning legislative
seats \citep[68]{Ames2001}. In Brazil, mayors are usually members of the largest
coalitions \citep{poulsen2018political}, thus there is an incentive for
candidates to side with the mayor before and after the election}." We mention
that information again on page 22, footnote 12: "\textit{The effect of city
council size on the number of mayor-aligned politicians stems from the rounding
rule adopted by the proportional representation system in Brazil. The rounding
rule favors the coalitions with more votes. Most of the time, the coalition of
the elected mayor is the one that receives more votes.}".

@@

We entirely agree with Reviewer 3 that we need to discuss the scope conditions
of our findings in more detail. We acknowledge that the external validity of
our results might be conditional on the contextual characteristics of our
study. We have rewritten two paragraphs in the Discussion (page 29) to highligh
the implication of our results. We write: "\textit{Our findings
have implications that extend well beyond Brazil. A general form of our
argument is that it is easy for a politician to negotiate with members of her
in-group \citep{abbink2019, g9030057}. Specifically, several
countries have separate executive and legislative powers, such as the federal
level of presidential systems, state governments, and local city councils. As
these institutions are influenced by political allegiances, the dynamics we
expose here may be generalizable. Depending on legislative support, changing
the legislature size could increase the chance of electing politicians that are
not aligned with the executive, hence decreasing welfare. Despite the
particular effects on political support and welfare, the logic described in
this paper would remain relevant for empirically accessing the effect of
enlarged legislatures on welfare. Our findings may also help scholars
understand why other countries in Latin America and Asia can generate effective
governance despite having strong executives and large coalitions
\citep{pereira2012surprising}.}".

>>>>

The second reason is that adding control variables improves the efficiency of
our estimates \citep{calonico2019regression}. We add five controls to the main
specifications. We include the 2003 population because it conditions the
multiple threshold assignments. We add GDP per capita to control for Brazil's
economic expansion during the 2000s. We also add the number of seats in 2000 to
ensure that our results come from the current legislature size and not from past
seat allocations. Year was included in the models to control for seasonal
effects. Finally, we add a dummy for Northeast states. The Northeast region
received considerable attention from the Federal Government in the 2000s.
According to \citet{de2015politica}, in 2003 the Lula administration recreated
the Superintendency for the Development of the Northeast (SUDENE), investing BRL
84 Billion from 2003 to 2010. This amounts to around 70\% of all targeted
regional investments. One example of these investments is that the Federal
Government created about 100 new universities in the Northeast region. Moreover,
infant mortality in the region decreased from 22.4 deaths per 1000 infants born
in 2005 to 19.6 deaths per 1000 infants born in 2008 due to larger federal
investments. In turn, education quality improved from 2.69 in 2005 to a 3.14
score in 2007 (0 to 10 quality of education score). For this reason, adding a
dummy for Northeast states is essential for ensuring the consistency and the
efficiency of our estimates.

@@

We collapse two concerns from Reviewer 3 since they both speak to core topics in
our paper. In Table 6 of the Supplementary Materials (page 21), we show that an
additional legislator usually does not lead to significant increases in public
expenditure. Therefore, our results speak more about the allocation of resources
than about government spending. In our section titled "Background on the
Brazilian Case" (page 14), we clarify why increasing the city council size often
results in a pro-mayor legislator. We write (page 15): "\textit{Brazil also
adopts a unique formula to allocate seats, which combines the Hare quota and the
D’Hondt method and strongly favors larger parties \citep{nicolau2015sistemas}.
This poses a major obstacle for small parties to reach the electoral quorum, so
they often join party coalitions to improve their chances of winning legislative
seats \citep[68]{Ames2001}. In Brazil, mayors are usually members of the largest
coalitions \citep{poulsen2018political}, thus there is an incentive for
candidates to side with the mayor before and after the election}." We mention
that information again on page 22, footnote 12: "\textit{The effect of city
council size on the number of mayor-aligned politicians stems from the rounding
rule adopted by the proportional representation system in Brazil. The rounding
rule favors the coalitions with more votes. Most of the time, the coalition of
the elected mayor is the one that receives more votes.}"

@@

We entirely agree with Reviewer 3 that we need to discuss the scope conditions
of our findings in more detail. We acknowledge that the external validity of
our results might be conditional on the contextual characteristics of our
study. We have rewritten two paragraphs in the Discussion (page 29) to highligh
the implication of our results. We write: "\textit{Our findings have
implications that extend well beyond Brazil. A general form of our argument is
that it is easy for a politician to negotiate with members of her in-group
\citep{abbink2019, alt2018giving}. Specifically, several countries have
separate executive and legislative powers, such as the federal level of
presidential systems, state governments, and local city councils. As these
institutions are influenced by political allegiances, the dynamics we expose
here may be generalizable. Depending on legislative support, changing the
legislature size could increase the chance of electing politicians that are not
aligned with the executive, hence decreasing welfare. Despite the particular
effects on political support and welfare, the logic described in this paper
would remain relevant for empirically accessing the effect of enlarged
legislatures on welfare. Our findings may also help scholars understand why
other countries in Latin America and Asia can generate effective governance
despite having strong executives and large coalitions
\citep{pereira2012surprising}.}".
